This work would not have happened without the people who have supported me throughout this journey.


I~am deeply grateful to my advisor, George Candea, an exceptional model of strength, vision, and kindness.
%
I~am indebted for his patience and wisdom, for pushing me out my comfort zone to become independent in pursuing my goals and reaching for the stars.  I feel very fortunate to having worked with him and I wouldn't have gotten this far without his mentorship.


I~thank my outstanding thesis committee: Vikram Adve, Johannes Kinder, Willy Zwaenepoel, and Jim Larus.  Their insightful comments and advice helped crystallize the vision of the thesis.


All the work presented here is the result of collaboration with many incredibly bright people.
%
I~am grateful to Johannes Kinder for his tenacious help with Chef.  During our many insightful discussions, he would bring clarity to the most difficult problems.
%
I~thank Vitaly Chipounov for helping me navigate the fine mechanics of the S2E system.
%
I~am indebted to Vlad Ureche, who was instrumental in Cloud9's successful encounter with real-world software.
%
I~thank Cristian Zamfir for his advice and patience during the most critical parts of my PhD.
%
I~thank Volodymyr Kuznetsov for his insights and for being a model of resourcefulness.
%
I~thank Martin Weber for his work and for withstanding my mentoring. 
%
I~am grateful to Liviu Ciortea for easing my way to symbolic execution.
%
I~thank Istvan Haller, Calin Iorgulescu, Ayrat Khalimov, and Tudor Cazangiu for their contributions to Cloud9.


My PhD experience was defined by the interactions I had with the phenomenal team in the Dependable Systems lab.
%
I~am truly grateful to
Silviu Andrica,
Radu Banabic,
Vitaly Chipounov,
Alex Copot,
Horatiu Jula,
Baris Kasikci,
Johannes Kinder,
Volodymyr Kuznetsov,
Georg Schmid,
Ana Sima,
Jonas Wagner,
Cristian Zamfir,
and
Peter Zankov
for the inspiring moments and making the lab a fun place to be.
%
I~am especially thankful to Nicoletta Isaac, who always made sure everything in the lab ran smoothly.


I~thank Ed Bugnion and Jim Larus for their inspiring advice and immensely useful lessons.
%
I~am thankful to Burak Emir and Lorenzo Martignoni, my mentors at Google, for their guidance and support.


I~thank Jonas Wagner for his precious help with translating the thesis abstract to German.
%
I thank Amer Chamseddine, Lo\"{\i}c Gardiol, Benjamin Schubert, and Martin Weber for their valuable feedback on my presentation dry-runs and their availability on a short notice.


I~am grateful to Cristian Cadar, Daniel Dunbar, and Dawson Engler for creating and open-sourcing KLEE.  Beside serving as a foundation for my own work, I learned a lot about symbolic execution by studying and tinkering with its code.


I~thank Google for generously supporting a significant part of my research through a fellowship.
%
I~thank EPFL for providing me a unique working environment and unparalleled resources to pursue my work.
%
I~thank ERC for their important financial support.


I~thank my parents, Jana and Mihai Bucur, for their selfless support and encouragement to follow my dreams.  Any of my accomplishments bears the mark of their upbringing.
%
I~thank my brother, Andrei Bucur, for his care and inspiration.


I~thank Alexandra Olteanu for her tireless support and care, for her wisdom, and for being a pillar of strength throughout the years.

%%% Local Variables: 
%%% mode: latex
%%% eval: (visual-line-mode)
%%% fill-column: 1000000
%%% TeX-master: "main"
%%% End:
