\section{Motivation}

\begin{itemize}
\item Real-world system applications use a rich set of OS abstractions: processes, threads, files, sockets, pipes, signals, etc.
\item Supporting these abstractions efficiently in a symbolic execution engine is challenging.
\item One alternative is to bundle them with the program and execute as one (S2E). Another alternative is to handle OS calls as external and concretize them (Klee).
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Environment Model Design}

\begin{itemize}
\item Our insight is that these primitives can be abstracted (modeled) with reasonable precision using a two-tiered approach: (1) A set of primitives built into the symbolic execution engine for address spaces, threads, and synchronization, and (2) A guest-level model built on top of these primitives.
\item Our model builds on top of KLEE.
\item We replaced operations from the C library with our own model, calling into the symbolic execution engine primitives.
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Symbolic Execution Engine Primitives}

\begin{itemize}
\item Discuss address spaces.
\item Discuss mulithreading and scheduling.
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{POSIX Interface Model}

\begin{itemize}
\item Discuss design decisions in building the POSIX model.
\item Discuss stream buffers and block buffers.
\item Give example of thread synchronization primitives.
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Symbolic Test Suites}

\begin{itemize}
\item Symbolic test suites are like unit tests, except for the additional interface for creating symbolic inputs and tweaking the settings of the symbolic environment.
\item Can be encapsulated and executed both symbolically and concretely (for replay purposes).
\item Symbolic POSIX environment: stream fragmentation, fault injection, symbolic scheduler.
\end{itemize}

%%% Local Variables: 
%%% mode: latex
%%% eval: (visual-line-mode)
%%% fill-column: 1000000
%%% TeX-master: "main"
%%% End:
