In this chapter, we describe the problem being addressed in this thesis and present a brief overview of the solution we propose.
%
Subsequently, in Chapter~\ref{ch:relatedwork}, we describe in more depth the prior art and the work related to ours, to gain an understanding of the landscape in which our solution appeared.
%
The rest of the thesis covers our solution.

\section{Problem Definition}
\input{introduction/problem}

\section{Solution Overview: A Tailored Approach to The Environment Problem}
\sectionmark{Solution Overview}
\input{introduction/solution}


\section{Thesis Roadmap}

The rest of the thesis presents in detail the design, implementation, and evaluation of the two approaches to the environment problem.

Chapter~\ref{ch:relatedwork} provides more background on symbolic execution and the environment problem, by surveying the related work and positioning our contributions with respect to it.

Chapter~\ref{ch:cloud9} expands on the idea of modeling the operating system interface.  It presents the core abstractions that are built into the symbolic execution engine, then elaborates on the specifics of modeling the POSIX interface on top of them.

Chapter~\ref{ch:chef} presents the approach of using interpreters as executable language specifications.  It presents an overview of the Chef system, then it goes into the details of converting between the low-level symbolic execution of the interpreter and the high-level program execution.

Chapter~\ref{ch:paas} presents the ongoing work and longer-term vision of building a cloud-based testing service for cloud applications based on the techniques introduced in this thesis.

Chapter~\ref{ch:evaluation} provides the experimental evaluation of the two systems we built, along two main dimensions: the effectiveness in generating test suites and finding bugs, and the scalability to real-world software.

Chapter~\ref{ch:conclusion} ends the thesis with conclusions.


\section{Previously Published Work}

This thesis includes material previously published in conference and workshop papers:

\begin{itemize}
\item Chapter~\ref{ch:cloud9}: Stefan Bucur, Vlad Ureche, Cristian Zamfir, and George Candea. Parallel Symbolic Execution for Automated Real-World Software Testing.  In \emph{ACM European Conference on Computer Systems (EuroSys)}, 2011.~\cite{cloud9}
\item Chapter~\ref{ch:chef}: Stefan Bucur, Johannes Kinder, and George Candea.  Prototyping Symbolic Execution Engines for Interpreted Languages.  In \emph{ACM International Conference on Architectural Support for Programming Languages and Operating Systems (ASPLOS)}, 2014.~\cite{chef-se}
\item Chapter~\ref{ch:paas}: Stefan Bucur, Johannes Kinder, and George Candea.  Making Automated Testing of Cloud Applications an Integral Component of PaaS.  In \emph{ACM SIGOPS Asia-Pacific Workshop on Systems (APSys)}, 2013.~\cite{paas-testing}
\end{itemize}

%%% Local Variables: 
%%% mode: latex
%%% eval: (visual-line-mode)
%%% fill-column: 1000000
%%% TeX-master: "main"
%%% End:
